### 2012-10-04 inst/examples/multiple_uncertainty.Rmd
trying larger grid to remove edge effects
testing `SDP_multiple_uncertainty` function (3-matrices based approach)
Comparing source of noise (coarse grid)

``` {r  echo=FALSE, cache=FALSE }
#opts_knit$set(upload.fun = socialR::flickr.url)
#options(device = function(width = 5, height = 5) 
#                   pdf(NULL, width = width, height = height))
````

@@

``` {r }
xmin <- 0
xmax <- 150
grid_n <- 150
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- 0.5
sigma_m <- 0.5
sigma_i <- 0.5
````

@@

```{r }
sdp <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, sigma_g, pdfn, sigma_m, sigma_i)
```

```{r }
mult <- find_dp_optim(sdp, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
```

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)

policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], new = mult$D[,1]), id = "stock")
ggplot(subset(policy, stock < 120)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable), shape="+")

dat <- subset(policy, stock < 120)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,120, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```

>>>>

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
#options(device = function(width = 5, height = 5) 
#                   pdf(NULL, width = width, height = height))
````

@@

``` {r }
xmin <- 0
xmax <- 200
grid_n <- 40
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
````

@@

```{r }
sdp_g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, .5, pdfn, 0, 0)
sdp_m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, .5, 0)
sdp_i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, 0, .5)
opt_g <- find_dp_optim(sdp_g, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
opt_m <- find_dp_optim(sdp_m, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
opt_i <- find_dp_optim(sdp_i, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
```

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
XMAX <- 140
policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], growth = opt_g$D[,1], meas = opt_m$D[,1], imp = opt_i$D[,1]), id = "stock")
ggplot(subset(policy, stock < XMAX)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable))

dat <- subset(policy, stock < XMAX)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,XMAX, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	geom_jitter(aes(x,y, color=variable), shpae='+') +
  xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```
